Commit Rater

### 2015-08-25 presentations/paper/methodology.tex
Order and add commits to time table

\begin{table}[t]
    \begin{tabularx}{\textwidth}{@{}|Y|Y|@{}}\hline
        \textbf{Repository} & \textbf{Time to Rate} \\\hline
        101worker & 10 seconds \\\hline
        BadgeKit & 4 seconds \\\hline
        perl & 3 minutes \\\hline
        Linux Kernel & 16 minutes\\\hline
    \end{tabularx}
    \caption{Time taken to clone repositories and rate their commits}
    \label{tab:time}
\end{table}

>>>>

\begin{table}[t]
    \begin{tabularx}{\textwidth}{@{}|Y|Y|Y|@{}}\hline
        \textbf{Repository} & \textbf{Commits} & \textbf{Time to Rate} \\\hline
        BadgeKit            & $723$            & $4$ seconds           \\\hline
        101worker           & $2073$           & $10$ seconds          \\\hline
        perl                & $60898$          & $3$ minutes           \\\hline
        Linux Kernel        & $543964$         & $16$ minutes          \\\hline
    \end{tabularx}
    \caption{Time taken to clone repositories and rate their commits}
    \label{tab:time}
\end{table}
